DNSKEY Management

### 2012-12-04 paper/paper.tex
outsourcing stuff

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant for such jitter: typically, if the \verb|epfl.ch| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch|'s DNS servers will appear as illegitimate whereas they perfectly are.

>>>>

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant to such jitter: typically, if the \verb|epfl.ch| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch|'s DNS servers will appear as illegitimate whereas they perfectly are, and this will last as long as Switch's servers do not reflect the update.

As suggested by some RFC\footnote{RFC 4641}, key updates should  happen at least every few months. Hence, it is crucial that a streamlined and reactive process is available for child-zones to notify their parent-zone when required. In the three R's setup, this means that the registry (or the registrars) must provide means for registrants to easily inform them of any changes regarding their DNSSEC keys.
%TODO process figure with Registrant -> Registrar -> Registry ?

Furthermore, as these communications concern the DNSSEC setup, security must be guaranteed: if a registry's update tools allow an attacker to update the key signatures, the whole point of DNSSEC is moot.

\paragraph*{Entity Roles Overlap} Another issue arises when we consider the fact that registrants may outsource part or whole of the hosting burden, like:

\begin{description}
\item[Key Signing] Services that will handle the zone signing and key rollovers are available\footnote{like this registrar: \url{http://registrars.nominet.org.uk/registration-and-domain-management/dns/dnssec-signing-service}}.
\item[Hosting] Countless hosting services are available, many of which are proposed by actual registrars. Some of them can also propose DNSSEC to their customers, in addition to the standard DNS service they also provide.
\end{description}

While having the registrars also handle DNSSEC will ease managing key rollovers and updates, it creates another problem: registrants, who generally are the registrars or registry's customers, might very well decide to switch from one service provider to another.

If standard DNS simply provides zone transfers as a mean enabling such migrations, DNSSEC must be treated differently. Whether a new private-public key pair is generated or whether the existing pair is transferred, new hurdles are introduced:

\begin{itemize}
\item[-] The transferred private key is not totally \emph{private} anymore, as now both the old and new service provider know it;
\item[-] Newly generated keys will require an update of the parent zone, and this might happen outside of normally planned rollover periods.
\end{itemize}

Another issue is that hosting and key signing services that are not registrars don't have to comply to any of ICANN's rules, increasing the difficulty to enforce common procedures, as none of these services is contractually bound to do so.
